
Codebook - Getting and Cleaning Data Project
========

Codebook was generated on 'r as.character(Sys.time())'. See also Readme.md for details of how this project was produced. 

The units of interest in this study are identifies according as according to the following variables: 

Subject: each subject has a unique subject identification number.
Activity: each subject was tested under the following conditions: 
        Walking
        Walking Upstairs
        Walking Downstairs
        Sitting
        Standing
        Laying


Measurement variables of the tidyData dataset
        ------------------------

For each subject/activity pair, the following measurements were taken. These measurements correspond to the column heacings in the tidyData dataset:
```{r, echo=FALSE}
names(tidyDataMeans)
```


Structure of the tidyData dataset
        ------------------------
```{r, echo=FALSE}
str(tidyDataMeans)
```

Example rows of the tidyData dataset
------------------------
```{r, echo=FALSE}
head(tidyDataMeans, n=5)
```

Summary of variables of the tidyData dataset
        ------------------------
```{r, echo=FALSE}
summary(tidyDataMeans)
```

